---
title: "Sandbox testing of Norming Experiment C (test only)"
author: "Menghan Yan and Florian Jaeger"
date: \today
geometry: margin=2cm
header-includes:
  - \usepackage{booktabs}
  - \usepackage{siunitx}
  - \usepackage{tabto}
  - \usepackage{soul}
  - \usepackage{xcolor}
  - \usepackage{placeins}
  - \usepackage{lscape}
  - \usepackage{animate}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \makeatletter\renewcommand{\fps@table}{!ht}\makeatother
  - \setstcolor{red}
  - \usepackage{sectsty}
  - \sectionfont{\color{blue}} 
  - \subsectionfont{\color{blue}}
  - \subsubsectionfont{\color{darkgray}}
output:
  pdf_document: 
    fig_caption: yes
    fig_width: 7
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes
    toc: yes
    toc_depth: 4
  fontsize: 10pt
---

# Prep for importing data

```{r, include=F}
library(knitr)

opts_chunk$set(dev = 'pdf',
               comment="", 
               echo=FALSE, warning=TRUE, message=TRUE,
               cache=FALSE, 
               size="small",
               tidy.opts = list(width.cutoff = 200),
               fig.width = 8, fig.height = 4.5, fig.align = "center")


def.chunk.hook  <- knitr::knit_hooks$get("chunk")
knitr::knit_hooks$set(chunk = function(x, options) {
  x <- def.chunk.hook(x, options)
  ifelse(options$size != "normalsize", paste0("\n \\", options$size,"\n\n", x, "\n\n \\normalsize"), x)
})

color_block = function(color) {
  function(x, options) sprintf('\\color{%s}\\begin{verbatim}%s\\end{verbatim}\\color{black}',
                               color, x)
}
knitr::knit_hooks$set(error = color_block('red'))
knitr::knit_hooks$set(warning = color_block('orange'))
```

```{r, include=F}
library(tidyverse)
library(magrittr)

library(gganimate)      # to animate plots
library(RColorBrewer)   # to select brewer colors
```

```{r, include=F}
options(width = 110)
```

```{r functions, include=FALSE}
source("functions-for-experiment-reports.R")
```

# Data import
```{r, message=F}
experiment = "experiment-A"

d.test = read_tsv("../../data/raw/experiment-NORM-A/sandbox/experiment-NORM-A-sandbox.results.batch1.tab")

d.test %<>%
  formatData(experiment = "NORM-A") %>%
  sortVars()
```


# Assessing the data

## How did DateTimeOffset work?
```{r}
d.test %>%
  select(ParticipantID, Answer.userDateTimeOffset, Answer.userDateTime) %>%
  group_by(ParticipantID) %>%
  unique()
```

## Does the data only contain test results (as it should)?

```{r}
nrow(d.test) == nrow(
  d.test %>% 
  filter(Phase == "test"))
```

## Have any participants taken the experiment more than once?

If a worker shows up more than once below, it is a duplicate take. For sandboxing, this is not an issue. We include this debugging step here since we will use it during production.

```{r}
d.test %>%
  group_by(workerid, Assignment.SubmitDateTime) %>%
  summarise() %>%
  group_by(workerid) %>%
  tally()
```

## Does each test block contain exactly 2 instances of each of the 6 audio conditions?


Show all combinations of participant, test block, and video condition for which this is *not* true:
```{r}
d.test %>%
  group_by(ParticipantID, Block, Condition.Test.Audio) %>%
  tally() %>%
  filter(n != 2) %>%
  nrow()
```
## Does each test block + test pen condition contain exactly 1 instance of each of the 6 audio conditions?

Show all combinations of participant, test block, and video condition for which this is *not* true:

```{r}
d.test %>%
  group_by(ParticipantID, Block, Condition.Test.Pen,Condition.Test.Audio) %>%
  tally() %>%
  filter(n != 1) %>%
  nrow()
```

## Does each test block contain exactly 3 instances of each of the 4 video conditions?

Show all combinations of participant, test block, and video condition for which this is *not* true:

```{r}
d.test %>%
  group_by(ParticipantID, Block, Condition.Test.OriginalLabel, Condition.Test.Pen) %>%
  tally() %>%
  filter(n != 3) %>%
  nrow()
```

## Does each test block contain exactly 1 instance of each video item?

Show all combinations of participant, test block, and video condition for which this is *not* true:

```{r}
d.test %>%
  group_by(ParticipantID, Block, ItemID) %>%
  tally() %>%
  filter(n != 1) %>%
  nrow()
```

## Matching beween YAML file and conditions in this data

 1. Get the HIT ID for each participant. 
```{r}
# In round 2, there were 5 distinct participants hitids, listed below.
 #382GHPVPHSR88OB2ODIRZUWIF2543L
 #3P520RYKCH6A31SLH2X2RVSWSBK5UZ                                      
 #3T6EIBTM9LONUYQ46T7SZ5WODMTAAY                                       
 #3UUIU9GZC55V3ODWHX7SMZ6U9XD5T8                                     
 #3W0XM68YZPVXCNMQM1ROII6HE4H1KG

# They acquired the same hittypeid, listed below
 #31IV7WI13BLON6VJBWVKSWVXG94H5R  

#checked: there are 5 completed assignments in the norming test round2 
```
 
 2. Got to the YAML success file (.success.yaml). 
 3. Look up that HIT ID.
 4. Count what *k*th HIT corresponds to that HIT ID from the top of the success file (e.g., it might be the 6th HIT ID).
 
```{r}

```
 

# Session info
```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
