---
title:      "YOUR PAPER TITLE"
shorttitle: "YOUR SHORT TITLE"

author:
  - name          : YOUR NAME"
    affiliation   : Department of X, University of Y
    email         : YOUR\@EMAIL-ADDRESS.COM
  - name          : YOUR CO-AUTHOR
    affiliation   : Department of X, University of Y
  - name          : YOUR OTHER CO-AUTHOR
    affiliation   : Department of X, University of Y

# The following prints the current date (optional, set to false to remove).
date: true
classoption:
  - preprint # Set to "reprint" or "preprint" 
# The reprint style typesets the manuscript with two columns and 10pt font size.  
#  - NumberedRefs # Uncomment to use numbered references rather than the default author-year style.
#  - trackchanges # Uncomment to track changes in the manuscript. (Use with preprint option).
#  - 12pt # Uncomment this to check if you exceeded the 12 page limit. (Use with reprint option).
#  - TurnOnLineNumbers # Uncomment to add line numbers in reprint. (Use with reprint.)

# optional for preprints
preprint_notice: "AUTHORS, JASA"

abstract:
# Put your abstract here. Abstracts are limited to 200 words for
# regular articles and 100 words for Letters to the Editor. Please no
# personal pronouns, also please do not use the words ``new'' and/or
# ``novel'' in the abstract. An article usually includes an abstract, a
# concise summary of the work covered at length in the main body of the
# article.
  Communication is awesome. Everyone should study it ...

keywords:  "KEY-WORD1; KEY-WORD2; KEY-WORD3; ..."
bibliography:   ["latex-stuff/library.bib", "latex-stuff/r-references.bib"]

output:
  bookdown::pdf_book:
    base_format: rticles::jasa_article
    latex_engine: xelatex
    includes:
      in_header: latex-stuff/header-JASA.tex
    keep_tex: yes
# The Author-Year style is the default. If you want to use the numeric style,
# use "jasanum2.bst" instead.
biblio-style: jasaauthyear2.bst
---

<!-- This file is called index.Rmd so that citr's adding work across its child documents. -->

\setcounter{secnumdepth}{5}
\renewcommand{\thesubfigure}{\textbf{\Alph{subfigure})}}

<!-- THIS IS THE DOCUMENT THAT YOU USE FOR KNITTING. IT WILL KNIT ALL THE OTHER SECTIONS, TOO -->

```{r, include=FALSE, message=FALSE}
if (!exists("PREAMBLE_LOADED")) source("preamble-JASA.R")
```

```{r knitr-setup, include=FALSE}
# To keep figure sizes comparable across the paper, you can define a basic width and height (e.g., for each panel)
# and then refer to those variables in the knitr chunk options that describe the figure width and height for a 
# specific R chunk.
options(width = 200, digits = 2, OutDec = ".", tinytex.verbose = TRUE)
base.width = 1.33
base.height = 1.33

knitr::opts_chunk$set(
  echo = FALSE, message = FALSE, warning = FALSE, 
  results = "markup", cache = TRUE, cache.lazy = F,
  interval = .2,
  dev = c('cairo_pdf'), # default format of figures
  fig.align = "center", fig.height = base.height, fig.width = base.width,
  tidy.opts = list(width.cutoff=80), tidy=TRUE,
  # Use fig.process to rename figure files generated by R so that they comply with
  # the journal naming policies. Remember to name plot chunks with the format
  # "Figure1", "Figure2", etc... You will find the figure files in
  # `[...]_files/figure-latex/`.
  
  # The only figure formats allowed for submission are the following: `.pdf`, `.ps`, `.eps`, or `.jpg`.
  # Figure files must be named in this fashion:
  # `Figure\#.xxx`, where `\#` is the figure number and `xxx` is the file format
  # (`Figure1.eps`, `Figure2.jpg`, `Figure3a.ps`, `Figure3b.ps`, etc).
  out.width="\\reprintcolumnwidth",
  fig.process = function(x) {
    x2 = sub('-\\d+([.][a-z]+)$', '\\1', x)
    if (file.rename(x, x2)) x2 else x
  })

# Some useful formatting for warnings and error messages, so that they are not easily missed.
color_block = function(color) { 
  function(x, options) sprintf('\\color{%s}\\begin{verbatim}%s\\end{verbatim}\\color{black}', color, x) }
knitr::knit_hooks$set(error = color_block('red'))
knitr::knit_hooks$set(warning = color_block('orange'))
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
knitr::knit_hooks$set(inline = function(x) { if (is.numeric(x)) prettyNum(x, big.mark=",") else x })
```

```{r}
INCLUDE_TODO <- T           # switch on/off to get to do list.
```

```{r sec-to-do, child="section-TO-DO.Rmd", eval= if (INCLUDE_TODO) TRUE else FALSE}
```

\newpage 
\setcounter{page}{1}
\setcounter{section}{0}

The JASA LaTeX class depends on the LaTeX package "revtex4-2". If you are using a full LaTeX distro, you should make sure "revtex4-2" is installed, and install it if not:

 1.	In RStudio/R, install a tex distribution in R, easiest via the R library tinytex: 
   a.	install.packages(“tinytex”)
   b.	tinytex::install_tinytex()
 2.	Outside of RStudio/R, manually download revtex4.2 an put it into the local tex folder (https://journals.aps.org/revtex)
 3.	In RStudio/R, update the tex tree: 
   a.	tinytex::tlmgr_update()
 4.	In RStudio/R, add any additional latex packages into the R markdown’s YAML header or a header.tex that’s references in the YAML header.
   a.	Avoid incompatibility between revtex 4.2 and latex packages like lscape and pdflscape (use latex package rotating for rotated tables; this package is already loaded as part of the JASA template)
   b.	Avoid incompatibility between JASA template and latex package subfigure by specifying \\usepackage[caption=false]{subfigure} or using the template’s function for multicomponent figure
   c.	Avoid fig.pos=”H” in R markdown chunks when forcing figure placement. Use fig.pos=”!h” instead.
   d. Do not load knitrExtra package since it loads several Latex packages that causes issues with revtex 4.1 and later


```{r, child="section-introduction.Rmd"}
```

```{r, child="section-general-discussion.Rmd"}
```

```{r, child="section-references.Rmd"}
```


\begin{acknowledgments}
Earlier versions of this work were presented at XXX meeting. We are grateful to OMITTED FOR REVIEW.
\end{acknowledgments}

\newpage

```{r, child="supplementary-information.Rmd"}
```
