<!-- Do NOT knit this document. It is part of a larger document. Instead knit the main document (my-apa-formatted-article) 
     If you want to separate the SI from the rest of the paper, we recommend you do so AFTER knitting them into a single PDF. 
     This will make sure that all references to sections, figures, tables, etc. are working as intended. You can easily separate 
     the PDF into two parts, using e.g., Acrobat PDF viewer. //-->
     
\setcounter{page}{1}

# Supplementary information {-}
\singlespacing

\setcounter{section}{0}
\setcounter{footnote}{0}
\setcounter{figure}{0}
\setcounter{table}{0}
\setcounter{equation}{0}
\renewcommand{\thesection}{\S \arabic{section}}
\renewcommand{\theHsection}{sisection. \arabic{section}}
\renewcommand{\thefootnote}{S\arabic{footnote}}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\renewcommand{\theequation}{S\arabic{equation}}

\changelocaltocdepth{3}
\tableofcontents

# Required software {#sec:software}
Both the main text and these supplementary information (SI) are derived from the same R markdown document available via [ADD-URL](OSF). It is best viewed using Acrobat Reader. The document was compiled using \texttt{knitr} [@R-knitr] in RStudio with R:

```{r}
version
```

You will also need to download the IPA font [SIL Doulos](https://software.sil.org/doulos/download/) and a Latex environment like (e.g., [MacTex](https://tug.org/mactex/mactex-download.html) or the R library \texttt{tinytex}).

We used the following R packages to create this document: `r papaja::cite_r("latex-stuff/r-references.bib", omit = T, pkgs = c("RJ-2021-048"))`. If opened in RStudio, the top of the R markdown document should alert you to any libraries you will need to download, if you have not already installed them. The full session information is provided at the end of this document.

## Interested in using R markdown do create APA formatted documents that integrate your code with your writing?
A project template, including R markdown files that result in APA-formatted PDFs, is available at [https://github.com/hlplab/template-R-project](https://github.com/hlplab/template-R-project). Feedback welcome. We aim to help others avoid the mistakes and detours we made when first deciding to embrace literal coding to increase transparency in our projects.

# Other sections

# Session Info

```{r session_info, echo=FALSE, results='markup'}
devtools::session_info()
```

